%%%
\documentclass[mathserif, aspectratio=43]{beamer}

\usetheme{metropolis}

\metroset{progressbar=frametitle}

\usefonttheme{professionalfonts}
\usepackage{mathtools}
\usepackage{mathspec}

\makeatletter % undo the wrong changes made by mathspec
\let\RequirePackage\original@RequirePackage
\let\usepackage\RequirePackage
\makeatother

\setmathfont{Latin Modern Math}
\usepackage[none]{hyphenat}

%%% Packages section %%%
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{tikz}
\usepackage{minted}

%%% Preamble %%%
\title{Machine Learning and Data Mining}
\subtitle{Course logistics}
\author{Maxim Borisyak}

\institute{National Research University Higher School of Economics (HSE)}
\usepackage{amsmath}


\begin{document}

\begin{frame}[plain]
	\titlepage
\end{frame}

\begin{frame}[fragile]
\frametitle{Structure}
{\Large
\texttt{github.com/HSE-LaMBDA/mldm-2018}
}

\end{frame}


\begin{frame}[fragile]
\frametitle{Course}
Two parts:
\begin{itemize}
\item traditional learning;
\item deep learning.
\end{itemize}

\end{frame}


\begin{frame}[fragile]
\frametitle{Home Assignments}
3 home assignments ("homeworks"):
\begin{itemize}
\item each consist of a number of exercises;
\item 2 weeks for submitting homework;\begin{itemize}
\item each additional week: 0.25 points penalty;
\end{itemize}

\item final score for an assignment:
$$\max \left[ 1, \sum_i \mathrm{exercise}_i \right] - \mathrm{penalty}$$
\end{itemize}
\begin{center}
\textbf{
  Home assignments must be your own work. \\
  Tools allowed for use will be specified in homework descriptions.
}
\end{center}

\end{frame}


\begin{frame}[fragile]
\frametitle{Exam}
\vspace*{5mm}
Exam:
\begin{itemize}
\item a presentation on Machine Learning challenge you took part in:\begin{itemize}
\item a non-trivial solution;
\item elaborate on method/features/... you chose.
\end{itemize}

\item overview of an advanced Machine Learning paper:\begin{itemize}
\item some suggestions will be on lectures (under Further Reading etc);
\item a list of preapproved advanced papers will be provided.
\end{itemize}

\end{itemize}
\begin{center}
\textbf{ \large Please, discuss your choice with me beforehand,\\ send me paper/draft of your presentation in advance.}
\end{center}

\end{frame}


\begin{frame}[fragile]
\frametitle{Final grades}
$$\text{Final grade} = 50\% \cdot \text{homeworks} + 50\% \cdot \text{exam}$$

$$\text{Final grade} = \left\lceil \frac{5}{3} \cdot \text{homework score} + \frac{1}{2} \cdot \text{exam score} \right\rceil$$where:
\begin{itemize}
\item homework score - sum of all marks for the homeworks (max 1 per each, max 3 in total);
\item exam score - mark on the exam, max 10.
\end{itemize}

\end{frame}


\begin{frame}[fragile]
\frametitle{Literature}
\begin{itemize}
\item Friedman J, Hastie T, Tibshirani R. The elements of statistical learning. New York, NY, USA:: Springer series in statistics; 2001.
\item Bishop C. Neural networks for pattern recognition. Oxford university press; 1995 Nov 23.
\item Bishop C. Pattern recognition and machine learning.
\end{itemize}

\end{frame}


\begin{frame}[fragile]
\frametitle{Deep Learning course}
There is an excellent course on Deep Learning:
\begin{itemize}
\item \url{https://www.hse.ru/edu/courses/222120421}
\end{itemize}
which intersects heavily with the program of this course.\\[5mm]
If \textbf{all} students agree:
\begin{itemize}
\item to attend the Deep Learning course;
\end{itemize}
then:
\begin{itemize}
\item this course will be devoted to advanced topics;
\end{itemize}
otherwise:
\begin{itemize}
\item an 'ordinary' (and compressed) Deep Learning course will be presented.
\end{itemize}

\end{frame}

\end{document}
